---
title: "RV"
author: "Collaborative project"
date: "4/9/2021"
output: pdf_document
---

```{r}
library(tidyquant)
library(tidyverse)
```

```{r}
head(FANG)
```

## Comments by Martín in italics.

### Natalia.

1. *I recommend using the pre-loaded FANG database as it is (with the corresponding length). Here, Natalia downloaded the data and took the first months of the 2021 year. She includes two plots. Are both plots the same? I would recommend adding some comments to understand the plots. Also, remember the objective is to link the volume with the returns as explained in the instructions (readme repo). Martín.*

2. *This is much better Natalia. I understand the value of the trend, it is useful, and it is a good idea to incorporate it. I agree with your contribution. However, the trend in loess reduces some detail which may be important later, when you link volume with stock returns. Ideally, this is where others start contributing to the project.*

### Gonzalo.

1. *Interesting piece of evidence. Looks good and it was important to look at this at this moment. However, more questions arise. First, I recommend using ggplot to be consistent with the class and the previous analysis. The ggplot also will allow you to show differences by stocks. Gonzalo took all stocks together and there might be differences between them. There might also be differences by year. There is something else that could bring more contributions on board, this is to compare returns not only with respect to volume but changes in the volume (percentage changes). Just as you do a percentage change in price you can also calculate percentage change in volume. This will allow you to compare both variables under the same units.*


## FANGs Volume in Recent Years.

Looking at volume patterns over time can help get a sense of the conviction behind rises and falls in specific stocks and entire markets, for that reason it is proposed to analyze the volume charts for each FANG stock, in order to understands its trend and then relate it with the stocks' returns.

```{r}
FANG %>%
ggplot(aes(x = date, y = volume, group = symbol)) +
    geom_segment(aes(xend = date, yend = 0, color = volume)) + 
    geom_smooth(method = "loess", se = FALSE) +
    labs(title = "FANG Volume Chart", 
         subtitle = "Daily Volume from 2013-2017", 
         y = "Volume", x = "") +
  facet_wrap(~ symbol, ncol = 2, scale = "free_y") +  
  theme_tq() +
    theme(legend.position = "none") 
```
The chart above shows the daily volumes and their trend line of FANGs stocks in the last few years. The bars represent the number of shares traded daily, and the line represents the trend that the volumes of each share have followed from 2013-2017.

It is clear that to analyze daily volumes, and see their highest and lowest points, it is necessary to have a graph focused on a shorter period of time, in order to obtain more clarity in the data and get more objective interpretations.

Still, trend lines are useful for analyzing data over long periods of time.In the graph, it is observed that FB, NFLX and GOOG stocks' volume has had a negative behavior, meaning that from 2013 to 2017 the average volume of shares decreased. In the case of FB, it is important to highlight that at the beginning it had a positive behavior, but at the end of 2014 it took a downward trend.In contrast, the trend line for AMZN looks stable throughout that period, so we infer that it has maintained a constant average in its volumes.

Now, it is proposed to analyze the a graph that shows the volumes by price

## correlation between daily volume and daily returns

```{r}

FANG_daily_returns <- FANG |>
  group_by(symbol) |>
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "daily",
               type = "arithmetic")


plot(FANG_daily_returns$daily.returns~FANG$volume)


```

Thanks to the scatter diagram, we can see that the relationship between daily returns and the volume of FANG have an independent and non-linear relationship. We can interpret it this way because their correlation coefficient is very close to zero (0.1356115) and its diagram does not indicate any curves. This coefficient can be seen below:

```{r}

cor.test(FANG_daily_returns$daily.returns, FANG$volume)
```
Thus, we could conclude that the return of a stock has not relationship with its volume in stock market; these variables are independent.
 
Does anyone disagree? or someone to improve my conclusion
